---
title: "FTIR_Absorbance"
author: "Marife Anunciado"
date: "April 27, 2017"
output: 
  github_document: default
vignette: >
  %\VignetteIndexEntry{FTIRAbsorbance}
  %\VignetteEngine{knitr::rmarkdown}
  %\usepackage[utf8]
---

```{r setup, include=FALSE}
mulch_plot <- read.csv("TN_BIOAGRI_204_Normalize.csv")
```

```{r include=FALSE}
library(dplyr)
library(ggplot2)
library(knitr)
library(tibble)
library(dplyr)
library(reshape2)
library(magrittr)
```

#### For each column, values were normalized. The cbind statement creates a new object/column of row means where "x" is the input matrix, row.means = rowMeans(x)" uses the rowMeans function to the matrix, and names the new column "row.means" so now we can make our new object with a column of row means. Since original wavelength values were converted as character, a new column "Wavelength" was added for plotting the 
absorbance purpose.

```{r, echo=FALSE, warning=FALSE}
normalize_add_rowmeans <- function(x) {
  for (i in 1:ncol(x)) {
        x[,i] <- (x[,i]- min(x[,i], na.rm = TRUE)) / (max(x[,i],na.rm = TRUE)-min(x[,i], na.rm = TRUE))
      }
      x <- cbind(x,row.means = rowMeans(x)) 
      x <-  add_column(x, Wavelength = 4000:600)
} 
a <- as.data.frame(normalize_add_rowmeans(mulch_plot))
knitr::kable(head(a))
```

```{r}
a <- as.data.frame(normalize_add_rowmeans(mulch_plot))
```

#### The plot only shows the absorbance of plastic materials on a particular wavelength.

```{r, echo=FALSE, warning=FALSE}
plot_abs <- function(df, df_x, df_y, xname,yname,title) {
    df <- ggplot(df) + geom_line(aes(df_x,df_y, colour = "red")) +
      xlab(deparse(substitute(xname))) + #user can assign a name on the x-axis label
      ylab(deparse(substitute(yname))) + #user can assign a name on the y-axis label
      ggtitle(deparse(substitute(title))) + #user can assign a plot title 
      theme_bw() + theme(legend.position = "none") 
      df
    print(df)} 
```

```{r}
plot_abs(a,a$Wavelength,a$C_38SAMPLE,xname = "Wavelength,nm", 
                   yname = "Absorbance, AU", title = "FTIR Spectra of Plastic Mulch") 
```

#### The plot below shows the absorbance of plastic materials on a particular wavelength with the acompanying compounds. 

```{r, echo=FALSE, warning=FALSE, results="asis"}
plot_abs_compounds <- function(df, df_x, df_y, xname,yname, title)
{
    df <- ggplot(df) + 
    geom_line(aes(df_x,df_y, colour = "red")) +
    xlab(deparse(substitute(xname))) + #user can assign a name on the x-axis label
    ylab(deparse(substitute(yname))) + #user can assign a name on the y-axis label
    ggtitle(deparse(substitute(title))) + #user can assign a plot title 
    theme_bw() + theme(legend.position = "none") 
    df <- df +
    annotate("text", x= 1800, y=1.1, label="C_O_Stretch", size =3.0) 
    df <- df +   
    annotate("text", x = 800, y = 1.0, label="O_H_Bend", size =3.0)
    df <- df + 
    annotate("text", x= 2994, y=0.3, label="C_H_Stretch", size =3.0)
    df
    print(df)}
```

```{r}
plot_abs_compounds(a,a$Wavelength,a$C_38SAMPLE,xname = "Wavelength,nm", 
                   yname = "Absorbance, AU", title = "FTIR Spectra of Plastic Mulch") 
```
